\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\TheLenaProject}

\author{Team 1, Team NAR
		\\Abeed Alibhai - alibhaa
		\\Rahul Bablani - bablanr
		\\Nezar Dimitri - dimitn
}

\date{}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 26th, 2016 & Team NAR & Rev0 - completed txt file\\ 
December 7th, 2016 & Team NAR & Rev1
\begin{itemize}
	\item converted txt file to LaTeX file
	\item fixed grammar and sentence structure
\end{itemize}
\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{Introduction}
\\
Images are like finger prints, each file has its own unique characteristics. Nonetheless, we all encounter the same problems with our digital images, repeatedly. Pictures can always use a little flavour and to tackle this problem we implemented photo filters such as gray scale, edge detection and invert to solve this problem. Whether you use images for entertainment or business this image processing application will fulfill your needs. Correcting these problems goes a long way toward improving your digital photo.

\section{Importance}

\\
Images are an importance factor within our life and society. Photos can mean cherishing memories while to others it could be their entire professional career. Photographers, directors, and artists all rely on photos and being able to alter those photos in different ways to their preference can be a game changer. Image filtering could be the difference between a home video and a Hollywood block buster. For some, it may just be a fun way to fight boredom and share your photos with all your friends on social media. What may seem to be such a trivial problem can prove itself to be more important and valuable depending on the individual's needs. 

\section{Context}
\\
The target of this project is to develop a program capable of importing and exporting an image. During the process the image can be processed into 3 different filters then exported into various available raster image formats. 
\\ \\
\noindent Stakeholders include: social media users (Instagram, Snapchat), photo/video editors, Team NAR (us) and future developers who may take over the project if it requires more man-power.
\\ \\
Our project will be be coded in the Java environment using the Eclipse IDE. For our GUI we will be implementing the JFrame library, and running the program as a Java application. To apply these filters we will be using the Marvin framework plugin. The program will be available to run on PC, Macintosh and Linux devices.


\end{document}